Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2023-03-08 paper-1/manuscript.tex
Added F9 legend

\begin{figure*}%
    \centering
    \includegraphics{fig9.pdf}
    \caption{}
    \label{fig9}
\end{figure*}
\textbf{Fig. 8} TODO

>>>>

\begin{figure*}%
    \centering
    \includegraphics{fig9.pdf}
    \caption{}
    \label{fig9}
\end{figure*}
\textbf{Fig. 10} Illustration of the origin of DD in our model.
\textbf{a} Left: In an oddball context, the regular inputs are encoded in the network by high local suppression, which reduces their overall response, leading to low global suppression. Deviant inputs encounter low local and global suppression and therefore evoke a large response. Right: In an irregular context, the network frequently encounters rare stimuli with low local suppression, leading to large overall responses and high global suppression, with these two (global response and suppression) counter-balancing each other. Deviant inputs encounter this high global suppression and therefore evoke smaller responses.
\textbf{b} Adding additional suppression (e.g., STD) affects these situations differently. Left: In an oddball context, the additional suppression further reduces the regular response, permitting even greater recovery of the wider network. Right: In an irregular context, global suppression is instead increased, and all responses reduced.
